Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-05-04 manuscript.Rmd
Uncited article plot functional.

foreward <- auto.arima(uncited.ts)
uncited.forecast <-data.frame(forecast(fit, 2))
forecast.estimated <- uncited.forecast$Point.Forecast
forecast.years <- c(2012, 2013)

@@

#articles.df.melted <- rbind(articles.df.melted, uncited.df)

ggplot(na.omit(articles.df.melted),  aes(Year, value, colour = variable)) + 
    geom_line() + 
    geom_point() + 
    scale_color_manual(values=cp) + 
    geom_point(data = uncited.df, aes(Year, value, colour = variable)) + 
    ylim(c(0, 2700))

>>>>

foreward <- auto.arima(uncited.ts)
uncited.forecast <-data.frame(forecast(foreward, 2))
forecast.estimated <- uncited.forecast$Point.Forecast
forecast.years <- c(2012, 2013)

@@

percent.df <- rbind(articles.df.melted, uncited.df)
percent.df.cast <- reshape2::dcast(percent.df, Year  ~ variable, value.var = "value")
percent.df.cast$estimate.code <- ifelse(is.na(percent.df.cast$Uncited.N), 
    "arima.Estimated", ifelse(!is.na(percent.df.cast$Uncited.N), "Scopus.Estimated", percent.df.cast$Uncited.N))

percent.df.cast$percent <- ifelse(!is.na(percent.df.cast$Uncited.N), percent.df.cast$Uncited.N/percent.df.cast$HD.N, ifelse(!is.na(percent.df.cast$Estimated), percent.df.cast$Estimated/percent.df.cast$HD.N, percent.df.cast$Uncited.N))

percent.df.cast$NoCites <- ifelse(is.na(percent.df.cast$Uncited.N), percent.df.cast$Estimated, 
                           ifelse(is.na(percent.df.cast$Estimated), percent.df.cast$Uncited.N, percent.df.cast$Uncited.N))

percent.cast.a <- select(percent.df.cast, Year, HD.N, NoCites)
percent.cast.b <- select(percent.df.cast, Year, estimate.code, percent)

percent.melt.a <- reshape2::melt(percent.cast.a, id.vars="Year")
percent.melt.b <- reshape2::melt(percent.cast.b, id.vars=c("Year", "estimate.code"))

percent.melt.b <- rename(percent.melt.b, variable2 = variable, value2 = value)
percent.melt.df <- full_join(percent.melt.a, percent.melt.b, by = "Year")

percent.text <- select(percent.melt.df, Year, value, value2, variable) 
percent.text <- percent.text %>% filter(variable != "HD.N")
percent.text$value2 <- round(percent.text$value2, digits=3) *100 
percent.text$value2 <- paste(percent.text$value2, "%", sep="")
percent.text <- percent.text[c(1, 7, 11, 16, 19, 22, 24),]

#percent.df.cast <- select(percent.df.cast, Year, estimate.code, percent) %>% filter(Year <= 2013)
#colnames(percent.df.cast) <- c("Year", "variable", "value")

cp <- c("#5e3c99","#e66101")

ggplot(na.omit(subset(percent.melt.df, subset=variable != "Scopus.N")), 
    aes(Year, value, colour = variable)) + 
    geom_line() + 
    geom_point() +
    scale_color_manual(values=cp, labels = c("Number of Articles Published", "Number of Uncited Articles \n(Past 3 Years)")) +
    geom_text(data = percent.text, aes(Year, value+40, label = value2), size=4, colour="black") + 
    ylim(c(0, 2200)) + 
    theme(legend.position="bottom") +
    theme(legend.title=element_blank()) +
    ylab("N")
